
R for Everyone Codebook 

---------------------------------
# Chapter4: Basic command
## 4.2. Variable

```{r}
x<--2
y=5
assign("j",4)
j
```

## 4.3 Data
### 4.3.1 Numerical data

```{r}
class(x) #"numeric"
is.numeric(x) #TRUE
i<-5L #integer
is.integer(i) #TRUE
is.numeric(i) #TRUE
class(4L) #integer
class(2.8) #numeric
```

### 4.3.2 Text data

```{r}
x<-"data"
y<-factor("data")
y<-"data"
class(x) #character
nchar(x) #4 = number of character
nchar(452) #3
nchar(y) #error - y requires a character vector
```

### 4.3.3 date

```{r}
date1<-as.Date("2012-06-28")
class(date1) #date
as.numeric(date1) #15519

date2<-as.POSIXct("2012-06-28 17:42")
date2
class(date2) #[1] "POSIXct" "POSIXt" 
as.numeric(date2) #[1] 1340872920
```

Lubridate, chron packages are used to treate time or date such as an object.
-as.numeric/as.date (): change the type of object
```{r}
class(date1) #date
class(as.numeric(date1)) #numeric
```

### 4.3.4 Logical 

logical is binary values eithrer TRUE(1) or FALSE (0)
```{r}
TRUE*5 #5
FALSE*5 #0

k<-TRUE
class(k) 
is.logical(k) #TRUE
2==3
2!=3
2<3
2<=3
"data" < "stat" #number of character
class("data")

```

#4.4 Vector
##4.4.1 vector calculation

We set the basic vector, and can calculate sum/deduct/devide without loop.

```{r}
x<-c(1,2,3,4,5,6)
x+2
x-3
x^2
sqrt(x)
```

c is the function to create a vector, and we can use ":" operator, to calculate sequential numbers. 
```{r}
1:10
10:1
-2:3
5:-7
```

Vector operator can be expanded (e.g., there are two vectors with same length, and computation of each vector components once).

```{r}
x<-1:10
y<--5:4
x+y
x-y
x/y  
x**y # x^y: x to yth power
length(x)
length(x*y)
```

Two vectors with different length needs more complex computation.
Generally, a vector with shorter length is used multiple times. 

```{r}
x+c(1,2)
x+c(1,2,3)

x<=5
x>y
```

All function is used to test whether all values satisfy comparative statistics. 
```{r}
x<- 10:1
y<- -4:5
all(x<y)
```
 
- nchar function is used toward each component of vector.
```{r}
q<-c("Hockey","Football","Baseball","Curling","Rugby",
     "Lacrosse", "Bascketball","Tennis","Cricket","Soccer")
nchar(q)
nchar(y)
```

To access vector coponent, [] is used. To extract first component of x vector, x[1], x[1:2] for first two components. If components to be extracted are not sequential, x[c(1.4)] expression is usefl.

```{r}
x[1]
x[1:2]
x[c(1,4)]
```

The [] expression works for numeric, logical, character classes. We can also name vector before/after making a vector.
```{r}
c(One="a",Two="y",Last="r")
w<-1:3
names(w)<-c("a","b","c")
w
```

### 4.4.2 Factor vector
Factor is a crucial concept to construct a model.
First, we add additional components to the vector q.

```{r}
q2<-c(q,"Hockey","LAcrosse","Hockey","Water Polo",
      "Hockey","LAcrosse")
```

We can transform this vector into factor by as.factor function.
```{r}
q2Factor<-as.factor(q2)
q2Factor
```

After q2Factor components are listed, levels are also listed. Factor's level lists non-duplicate figures. 

```{r}
as.numeric(q2Factor)
```

Geenrally, no attention to the order of levels is required for factor. In addition, all level are treated same. However, there are occations factor order becomes significant.Ordered argument is set TRUE so that factor is ordere according to level argument.
```{r}
factor(x=c("High School","College","Masters","Doctorate"),
       levels=c("High School","College","Masters","Doctorate"),
       ordered=TRUE)
```

Factor keeps identical items, we could reduce size of variables.

#4.6 Function command
apropos() is useful to search specific function by keyword
```{r}
apropos("mea")
?kmeans
```

## 4.7 Missing Value "Œ‡‘¹’l"
Missing value plays an important role for statistics and calculation. There are two types of missing values; NA and NULL.

### 4.7.1 NA
NA is shown as a component of vector. is.na() could test whether there is any missing value in vector.
```{r}
z<-c(1,2,NA,8,3,NA,3)
z
is.na(z)
```

NA can be input by inserting NA, and corresonds to every class of vector. 
```{r}
zChar<-c("Hockey",NA,"LAcrosse")
zChar
is.na(zChar)
```

‘½d‘ã“ü–@ is a popular method to deal with statistical analysis. Details is available in chapter 25 of "Data Analysis Using Regression and Multilevel/Hierachical Models".

### 4.7.2 NULL
NULL cannot be insite vector, as it disappears in the vector after its used. 
```{r}
z<-c(1,NULL,3)
z
```

NULL is not saved in the c vector.We can test if there is any NULL item by is.null function ().
```{r}
d<-NULL
is.null(d)
is.null(7)
```


---------------------------------
#Chapter 5: High level data structure
We can treat high dimentional/level data frame by R, with data.frame, matrix, list,array.

## 5.1. data.frame
data.frame is similar to excel spreadsheet with row/columns(obs - row, variables - columns).Each column has a same length vector, and can be treated with different class of data.The data.frame function () is frequently used to form data.frame.

```{r}
x<-10:1
y<--4:5
q<-c("Hockey","Football","Baseball","Curling","Rugby",
     "Lacrosse","Bascketball","Tennis","Cricket","Soccer")
theDF<-data.frame(x,y,q)
theDF
```

In the above code, 10*3 data.frame was formed. Each column name can be changed in the data.frame function.
```{r}
theDF<-data.frame(First=x, Second=y, Sport=q)
theDF
```

The data.frame is a complex obeject with multiple characters. To quickly check number of rows/colmns, nrow/ncolumn () functions are used.
```{r}
nrow(theDF)
ncol(theDF)
dim(theDF)
```

Name () function is used to check name of columns, and such column names can be changed easily. 
```{r}
names(theDF)
names(theDF)[3]

rownames(theDF)
rownames(theDF)<- c("One","Two","Three","Four","Five","Six","Seven","Eight","Nine","Ten")
rownames(theDF)
rownames(theDF)<-NULL
rownames(theDF)
```

head () function is useful for checking first few rows. class function () can be used to detect data.frame.
```{r}
head(theDF)
head(theDF,n=7)
tail(theDF)
class(theDF)
```

data.frame has each column as individual vector with different class, thus , thus we can access each column.For accesing specific row, argument "$" or "[]" could be used.

```{r}
theDF$Sport
theDF[3,2] # For [], we need to input row/column no.
theDF[3,2:3]
theDF[c(3,5),2] #row3, 5 with column 2
theDF[,c("First","Sport")]
```

```{r}
#Sport column only
theDF[,"Sport"]
class(theDF[,"Sport"]) #factor is reverted as its only one column
theDF["Sport"]
class(theDF["Sport"])
```

drop=FALSE is set if we want to extract noly one column data.frame with [].
```{r}
theDF[,"Sport",drop=FALSE]
class(theDF[,"Sport",drop=FALSE])
theDF[,3,drop=FALSE]
class(theDF[,3,drop=FALSE])
```

In section 4.4.2, factor is a special class, and we would like to confirm that such class can be exressed in data.frame as well.
- Model.matrix() is used with indicator variables (dummy).This results in 1 in case such row includes such level, otherwise 0.
```{r}

```

## 5.2 List

## 5.3 Matrix
matrix is a basic 

## 5.4 Array
Array is multidimentional vector. Array's components need to have same type. And [] can be used to access specific component,like Vector. In[], the first item is row number, second is column number etc. 

The difference between matrix and array is that array can be used for non-limited dimension, while matrix is limited to second dimension.

```{r}
theArray<-array(1:12,dim=c(2,3,2))
theArray
```

```{r}
theArray[1,,]
theArray[1,,1]
theArray[,,1]
```


---------------------------------
# Chap7: Statistical Graph
## 7.1 Basic graphics

### 7.1.1. Histogram
```{r}
require(ggplot2)
data(diamonds)
head(diamonds)
```

```{r}
hist(diamonds$carat, main="Carat Histgram",xlab="Carat")
```


### 7.1.2 Scatterplot
```{r}
plot(price~carat, data=diamonds)
plot(diamonds$carat, diamonds$price)
```

### 7.1.3 Boxplot
```{r}
boxplot(diamonds$carat)
```

## 7.2 ggplot2
###7.2.1 Histgraom Density chart by ggplot
```{r}
ggplot(data=diamonds)+geom_histogram(aes(x=carat))
```

```{r}
ggplot(data=diamonds)+geom_density(aes(x=carat), fill="grey50")
```

### 7.2.2. Scatterplot by ggplot
```{r}
ggplot(diamonds, aes(x=carat,y=price))+geom_point()
g<-ggplot(diamonds,aes(x=carat,y=price))
g+geom_point(aes(color=color))
g+geom_point(aes(color=color))+facet_wrap(~color)
g+geom_point(aes(color=color))+facet_grid(cut~clarity)
```

### 7.2.3 Boxplot by ggplot
```{r}
ggplot(diamonds, aes(y=carat, x=1))+geom_boxplot()
ggplot(diamonds, aes(y=carat,x=cut))+geom_boxplot()
```
















